Compare pseqs

### 2019-10-04 comparepseqs.Rmd
Beta plot show significance
Minor

    if (length(missing) > 0) {

        pseq <- import_filter_data(rds[[key]],
                                   included = c("MEN", "BL_AGE", "SYSTM", "DIASM", "BMI",
                                                "CURR_SMOKE", "BL_USE_RX_C09",
                                                "Q57X", "BL_USE_RX_C03",
                                                "BL_USE_RX_C07", "BL_USE_RX_C08"))
        dset <- meta.merge.alphadiversity(pseq) %>%
            mutate(diversities_shannon = as.numeric(scale(diversities_shannon)))

>>>>

    if (length(missing) > 0) {
        pseq <- import_filter_data(rds[[key]],
                                   included = c("MEN", "BL_AGE", "SYSTM", "DIASM", "BMI",
                                                "CURR_SMOKE", "BL_USE_RX_C09",
                                                "Q57X", "BL_USE_RX_C03",
                                                "BL_USE_RX_C07", "BL_USE_RX_C08"))
        dset <- meta.merge.alphadiversity(pseq) %>%
            mutate(diversities_shannon = as.numeric(scale(diversities_shannon)))
